Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-05-09 VegOzone.tex
Refine global irradiance paragraph

The average accumulated monthly precipitation $\sum_d\mathrm{Precip}$ indicates that winter and spring (November--April, except for March) are relatively dry ($\sum_d\mathrm{Precip} < 20\,\unit{mm}$). The driest month is January with $\sum_d\mathrm{Precip} = (16.7\pm 3.0)\,\unit{mm}$. The most precipitation occurs in the summer months, with a $\sum_d\mathrm{Precip} = (58.5\pm 9.2)\,\unit{mm}$ in August. The average annual accumulated precipitation ($\sum_m\mathrm{Precip}$) given with standard error of mean is $(383\pm 86)\,\unit{mm}$. Precipitation shows a large interannual variability.

The derived climatology for global irradiance ($Q_0$) at Svanvik (Appendix Fig.~\ref{fig:global_rad_clim}a)) in agreement with the geometrically derived sunshine duration (Supplement Fig.~\ref{fig:sunlight_fennoscandia}), approaches zero in December/January (polar night) and reaches its maximum in June/July (midnight sun conditions). The highest observed averaged daily maximum $\left<Q_0^\mathrm{max}\right>$ is about $800\,\unit{W\,m^{-2}}$, while on averaged daily mean $\left<Q_0^\mathrm{mean}\right>$ it is about $450\,\unit{W\,m^{-2}}$ (regularly reached in May--July). The maximum of the averaged daily minimum $\left<Q_0^\mathrm{min}\right>$ lies at about $200\,\unit{W\,m^{-2}}$.

>>>>

The average accumulated monthly precipitation ($\sum_d\mathrm{Precip}$) indicates that winter and spring (November--April, except for March) are relatively dry ($\sum_d\mathrm{Precip} < 20\,\unit{mm}$). The driest month is January with $\sum_d\mathrm{Precip} = (16.7\pm 3.0)\,\unit{mm}$. The most precipitation occurs in the summer months, with a $\sum_d\mathrm{Precip} = (58.5\pm 9.2)\,\unit{mm}$ in August. The average annual accumulated precipitation ($\sum_m\mathrm{Precip}$) given with standard error of mean is $(383\pm 86)\,\unit{mm}$. Precipitation shows a large interannual variability.

The derived climatology for global irradiance ($Q_0$) at Svanvik (Appendix Fig.~\ref{fig:global_rad_clim}a)) approaches zero in December/January (polar night) and reaches its maximum in June/July (midnight sun conditions). The highest observed averaged daily maximum ($\left<Q_0^\mathrm{max}\right>$) amounts to $800\,\unit{W\,m^{-2}}$, while the averaged daily mean ($\left<Q_0^\mathrm{mean}\right>$) is $450\,\unit{W\,m^{-2}}$ (regularly reached in May--July). The maximum of the averaged daily minimum ($\left<Q_0^\mathrm{min}\right>$) lies at about $200\,\unit{W\,m^{-2}}$.
